The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-02-17 paper/paper.tex
new plots

The Buzzard catalog was developed to support Dark Energy Survey Year 1 (DES-Y1)
data analysis, and is described in detail in \citet{buzzard}.  It used dark
matter simulations from L-GADGET2 \cite{lgadget} and then added galaxies using
the {\sc AddGals} algorithm \citet{addgals}, which matches a set of galaxy
property probability densities to data using sub-halo abundance matching. 
Buzzard galaxies extend to around redshift 2.3, and were shown to be a good
match (after appropriate selections) to DES-Y1 observable catalogs.  Magnitudes
using the LSST band passes were provided in the catalog.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1\linewidth]{results/initial_data.pdf}
\caption{The underlying number density $n(z)$ for the two catalogs used in the challenge,
after the initial cuts described in the text.}
\label{fig:initial_nz}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=1\linewidth]{results/colour_colour.pdf}
\caption{A colour-colour diagram for the two catalogs used in the challenge, showing the bands
available to participants.}
\label{fig:colour_colour}
\end{figure}

>>>>

The Buzzard catalog was developed to support Dark Energy Survey Year 1 (DES-Y1)
data analysis, and is described in detail in \citet{buzzard}.  It used dark
matter simulations from L-GADGET2 \cite{lgadget} and then added galaxies using
the {\sc AddGals} algorithm \citet{addgals}, which matches a set of galaxy
property probability densities to data using sub-halo abundance matching. 
Buzzard galaxies extend to around redshift 2.3 (significantly shallower than CosmoDC2)
and were shown to be a good
match (after appropriate selections) to DES-Y1 observable catalogs.  Magnitudes
using the LSST band passes were provided in the catalog.

@@

\begin{figure}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/initial_data.pdf}
\caption{The underlying number density $n(z)$ for the two catalogs used in the challenge,
after the initial cuts described in the text.}
\label{fig:initial_nz}
\end{figure}

\begin{figure}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/colour_colour.pdf}
\caption{A colour-colour diagram for the two catalogs used in the challenge, showing the bands
available to participants.}
\label{fig:colour_colour}
\end{figure}
